Score-based tests of measurement invariance: Use in practice

### 2013-09-09 frontiers/frontiers.Rnw
use mz-ordinal-proptest.R in simall-ordinal file. Update sim1 results
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@251 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{Results}
Full simulation results are presented in Figure~\ref{fig:sim11res} to
Figure~\ref{fig:sim13res}; all three test statistics exhibited 
similar results, with the unordered $\max\mathit{LM}$ 
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude for the first
factor loading $\lambda_{11}$, with panels reflecting the parameters 
being tested and lines reflecting $n$.
Figures~\ref{fig:sim12res} and Figure~\ref{fig:sim13res} display 
similar power curves when the factor covariance 
$\phi_{12}$ and error variance $\epsilon_{11}$ violate measurement
invariance, respectively.

>>>>

\subsection{Results}
Full simulation results are presented in Figure~\ref{fig:sim11res} to 
Figure~\ref{fig:sim13res}; all three test statistics exhibited 
similar results, with unordered  $\max\mathit{LM}$ demonstrated lower powers across all situations. ordered $\max\mathit{LM}$ and double-max exhibited equivalent power curves since there is only one parameter violating measurement invariance. Thus, different ways of aggregating $\bm B(\hat{\theta})$ would be the same.
Figure~\ref{fig:sim11res} displays power curves as a function of 
violation magnitude for the first
factor loading $\lambda_{11}$, with panels reflecting the parameters 
being tested and lines reflecting $n$.
Figures~\ref{fig:sim12res} and Figure~\ref{fig:sim13res} display 
similar power curves when the factor covariance 
$\phi_{12}$ and error variance $\epsilon_{11}$ violate measurement
invariance, respectively.
